Features of Accretion Phase Gravitational Wave Emission from Two-dimensional Rotating Core-Collapse Supernovae

### 2019-04-17 ref_response/ProjectNarrative.tex
Mansucript changes adressing Evan's comments

\pagestyle{fancy}
\fancyhf{}
\lhead{\fancyplain{}{PUT THE AAS JOURNALS MANUSCRIPT NUM HERE}}
\rhead{\fancyplain{}{M.A. Pajkos et al.}}
\rfoot{\fancyplain{}{\thepage}}

@@

\textbf{[4] For initial context, we include a reference to the relevant paper in the intro to account for 3D effects such as SASI and MRI.   At the end of Section 3.4, we include a warning that the presence of magnetic fields could cause instabilities that compromise the stability of post shock convection (ex. MRI).  }\\

@@

\textbf{[5] We acknowledge the small percentage of supernova progenitors that may have central angular velocities greater than 1 radian/sec.  Included in the introduction is an additional reference to de Mink et al. (2013) that shows the slim, yet distinct, possibility of rapidly rotating progenitors due to binary interactions.  We emphasize that this work is completed within the context of a controlled study.  While it is likely that the majority of CCSN progenitors are not rapid rotators, we justify our numerical choice because it allows us to clearly observe how the Solberg-Hoiland instability manifests itself and its specific influence on the GW signal.}\\

@@

\textbf{We agree that the GW signal and PNS evolution will be affected.  As a caveat, we add a reference to Muller et al. 2013 that points out that the peak GW frequency from GR effective potential is overestimated, compared to xCFC, while preserving the GW amplitude and PNS compactness (in beginning of Section 3.4).  Nevertheless, the GR effective potential has been shown to accurately reproduce results from the neutron star migration test (Marek et al. 2006, O'Connor \& Couch 2018).}\\

@@

\textbf{[10] This signal appears clearly as the bright region in Figure 6 for all rotational velocities and in Figure 11.  This fact is noted in Section 3.5.}\\

>>>>

\pagestyle{fancy}
\fancyhf{}
\lhead{\fancyplain{}{AAS15770}}
\rhead{\fancyplain{}{M.A. Pajkos et al.}}
\rfoot{\fancyplain{}{\thepage}}

@@

\textbf{[4] For initial context, we include a reference to the relevant paper in the intro to account for 3D effects such as SASI and MRI.   At the end of Section 3.4, we include a warning that the presence of magnetic fields could cause instabilities that compromise the stabilizing effects of rotation on the post shock convection (ex. MRI).  }\\

@@

\textbf{[5] We acknowledge the small percentage of supernova progenitors that may have central angular velocities greater than 1 radian/sec.  Included in the introduction is an additional reference to de Mink et al. (2013) that shows the slim, yet distinct, possibility of rapidly rotating progenitors due to binary interactions.  We emphasize that this work is completed within the context of a controlled study.  While it is likely that the majority of CCSN progenitors are not rapid rotators, we justify our numerical choice because it allows us to clearly observe how the Solberg-Hoiland criterion manifests itself and its specific influence on the GW signal.}\\

@@

\textbf{We agree that the GW signal and PNS evolution will be affected.  As a caveat, we add a reference to Muller et al. 2013 that points out that the peak GW frequency from GR effective potential is overestimated, compared to xCFC, while preserving the GW amplitude and PNS compactness (in beginning of Section 3.4).  Nevertheless, the GR effective potential has been shown to reproduce certain elements of the neutron star migration test, when compared to GR (Marek et al. 2006, O'Connor \& Couch 2018).}\\

@@

\textbf{[10] This signal appears clearly as the bright region in Figure 6, within the first 25 ms pb, for all rotational velocities and in Figure 11.  This fact is noted in Section 3.5.}\\
